IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-07 review/response_2.tex

		\begin{response}
			Please refer to Response~\ref{re:2.3}.
		\end{response}
	\end{editor}

	\begin{reviewer}
		\begin{point}
			As this paper proposed a BCD-based algorithm and LC-BCD algorithm, it could be better if the authors can further discuss the complexity and provide some measurements or some simulation results.
		\end{point}

		\begin{response}
			We appreciate your suggestion and agree that complexity analysis is necessary in algorithm evaluation.

			For SCA Algorithm~\ref{M-al:sca}, in the previous manuscript, we applied SCA on $t_{\mathrm{I},0} t_{\mathrm{P},0}$ at iteration $i$ as
			\begin{align}
				t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
				& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2,
			\end{align}
			which is feasible for any $t_{\mathrm{I/P},0}^{(i)} \in \mathbb{R}$ and widely adopted when $t_{\mathrm{I},0}$ and $t_{\mathrm{P},0}$ are variables. Hence, we claimed Algorithm~\ref{M-al:sca} `is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{M-eq:z_irs_approx}'. During revision, we realized that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ are essentially linear real expressions related to optimization variable $\boldsymbol{\Phi}$, and the SCA can be further reduced to
			\begin{equation}
				t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)} \ge t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}.
			\end{equation}
			Therefore, the quadratic term in the objective function \eqref{M-eq:z_irs_approx} is eliminated and the updated problem~\ref{M-op:irs} is indeed an SDP. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{M-Luo2010}. We have revised the manuscript as follows.
			\begin{framed}
				The passive beamforming design is summarized in the SCA Algorithm~\ref{M-al:sca}, where the relaxed problem \eqref{M-ob:irs}--\eqref{M-co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{M-al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{M-Luo2010}.
			\end{framed}

@@

			For GP Algorithm~\ref{M-al:gp}, the computational complexity is exponential w.r.t. the number of subbands \cite{M-Chiang2005}.
			\begin{framed}
				The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{M-al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{M-Chiang2005}.
			\end{framed}

			For M-SCA Algorithm~\ref{M-al:m_sca}, each optimization problem involved is an SDP with $(L+1)$ variables and linear constraints, and the computational complexity is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$ where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations.
			\begin{framed}
				Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{M-al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{M-Luo2010}. Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.
			\end{framed}

@@

			For BCD Algorithm~\ref{M-al:bcd}, since Algorithm~\ref{M-al:gp} is involved per iteration, the computational complexity is exponential w.r.t. the number of subbands.
			\begin{framed}
				The steps are summarized in the BCD Algorithm~\ref{M-al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{M-al:gp}.
			\end{framed}

			For LC-BCD Algorithm~\ref{M-al:lc_bcd}, both waveform and active beamforming are obtained in closed form, and the computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
			\begin{framed}
				The computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
			\end{framed}
			\label{re:1.1}
		\end{response}

@@

		\begin{point}
			Since this paper focused on IRS-aided SWIPT systems, it could be better if the authors can further enrich the survey part to make the paper more comprehensive. In particular, some papers have considered this kind of problem from a different aspect such as \cite{Xu2021}. It is kindly suggested to briefly discuss the main difference between \cite{Xu2021} and the problem considered in this paper.
		\end{point}

		\begin{response}
			Thank you for sharing this paper. Instead of optimizing the phase shift of each IRS element, it tailored a tile-based two-stage optimization framework for large-scale IRS to enable a flexible performance-complexity tradeoff. The model also adapts well to practical IRS models accounting AoA and AoD. We would like to kindly highlight that \cite{Xu2021} was not available at the time of submission of this manuscript. \cite{Xu2021} was indeed submitted in April 2021, i.e. several months after our submission to TCOM in Nov 2020. We therefore believe it is for authors of \cite{Xu2021} to further enrich the survey part of their manuscript by making it more comprehensive and discuss the difference between \cite{Xu2021} and this paper. Nevertheless to address the reviewer comments, we now compare with \cite{Xu2021c} which appeared on arXiv shortly before our submission.
			\begin{framed}
				Based on practical IRS and energy harvester models, \cite{M-Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization is divided into a reflection mode design stage and a joint reflection mode selection and precoder design stage. The proposed framework provides a flexible balance between performance and complexity.

@@

				\textellipsis To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with practical co-located information decoder and energy harvester.
			\end{framed}
		\end{response}

		\begin{point}
			It could be better if the authors can provide some references for the parameter values chosen in the simulation part.
		\end{point}

		\begin{response}
			The system layout follows \cite{M-Wu2019}. For the center frequency, we consider \SI{2.4}{\GHz} due to its ubiquitous and license-free properties. Note that the path loss can be greatly reduced (and the R-E performance can be improved) if the system operates at much lower frequency, as considered in most IRS papers. In the previous manuscript, we made a mistake in the choice of reference path loss. As indicated by Comment~\ref{pt:3.3}, even the free-space path loss should be around \SI{40}{\dB} at \SI{1}{\meter}. To fix this issue, we updated the path loss model as IEEE TGn channel model D that is representative of small environments such as residential homes and small offices \cite{M-Erceg2004}. It has three clusters with \SI{50}{\ns} r.m.s. delay spread, and the path loss exponent is \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and \num{3.5} onwards to further penalize channels with large distance. We also raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi}. As for the rectenna parameters, the parameters are taken from \cite{M-Clerckx2016a} and the reference have been added to the revised manuscript.
		\end{response}

@@

		\begin{point}
			The reviewer noticed that in Algorithm~\ref{M-al:lc_bcd}, there are two convergence criteria. It could be better if the authors can briefly interpret this issue.
		\end{point}

		\begin{response}
			We incorporated two cases (WIT/non-WIT) into Algorithm~\ref{M-al:lc_bcd}, where Algorithm~\ref{M-al:m_sca} is called during each iteration. To obtain the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC current \eqref{M-eq:z_irs_approx} should be maximized, such that the current expression is dropped and no SCA is involved. To clarify this point, we have updated the description on Algorithm~\ref{M-al:m_sca} as follows.
			\begin{framed}
				Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes. The rate constraint \eqref{M-co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$. To achieve the WIT point ($\rho=0$), the rate \eqref{M-eq:R_irs} should be maximized, the current expression \eqref{M-eq:z_irs_approx} should be dropped, and no SCA is involved.
			\end{framed}
			Correspondingly, to achieve the WIT point, the LC-BCD Algorithm~\ref{M-al:lc_bcd} should maximizes $R$ instead of $z$. Line~\ref{li:convergence_begin}--\ref{li:convergence_end} was modified to avoid ambiguity and Algorithm~\ref{M-al:lc_bcd} is indexed below by \ref{al:lc_bcd} .
			\begin{algorithm}[!h]
				\caption{LC-BCD: Waveform and Beamforming.}
				\label{al:lc_bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{M-eq:w}
					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{M-eq:R_waveform}, \eqref{M-eq:z_waveform}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{M-al:m_sca}
						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{M-eq:h_n}, \eqref{M-eq:b_n}
						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{M-eq:s_i}, \eqref{M-eq:s_p}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{M-eq:w}
						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{M-eq:R_waveform}, \eqref{M-eq:z_waveform}
						\If{$\rho=0$} \label{li:convergence_begin}
							\State $\Delta = R^{(i)} - R^{(i-1)}$
						\Else
							\State $\Delta = z^{(i)} - z^{(i-1)}$
						\EndIf
					\Until $\lvert \Delta \rvert \le \epsilon$ \label{li:convergence_end}
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
				\end{algorithmic}
			\end{algorithm}
			The description on Algorithm~\ref{M-al:lc_bcd} have been updated as follows.
			\begin{framed}
				To achieve the WIT point ($\rho=0$), the rate \eqref{M-eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnotemark Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to maximum capacity $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
			\end{framed}
			\footnotetext{Recall in Remark~\ref{M-re:subband_tradeoff} that different subchannel designs lead to different capacities.}
			\label{re:1.4}
		\end{response}
	\end{reviewer}

@@

			Next, we verify the last observation where the expectation of the DC current scales quartically with $L$ in a much simplified scenario. Consider a SISO WPT system in a frequency-flat channel. We assume a sufficiently large $L$ such that the auxiliary link is dominant and the contribution of direct channel is omitted. With uniform power allocation to multisine ($s_{\mathrm{P},n} = \sqrt{2P}/\sqrt{N}$) in the frequency domain, the DC current writes as
			\begin{equation}
				z_{\mathrm{UP}} = \beta_2 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^2 P + \frac{3}{8} \beta_4 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^4 F,
			\end{equation}
			where $\beta_2$ and $\beta_4$ are fixed rectenna parameters, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$ are the path loss of incident and reflected links, $X$ is the random variable that models the small-scale double fading through one IRS element at any subband, and
			\begin{equation}
				F = \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} s_{n_1} s_{n_2} s_{n_3} s_{n_4} = \frac{4(2N^2+1)}{3N} P^2.
			\end{equation}
			Taking expectation over $\lvert X \rvert$, we have
			\begin{equation}
				\bar{z}_{\mathrm{UP}} = \beta_2 \Lambda_{\mathrm{I}}^2 \Lambda_{\mathrm{R}}^2 L^2 \mathbb{E}\{\lvert X \rvert^2\} P + \frac{3}{8} \beta_4 \Lambda_{\mathrm{I}}^4 \Lambda_{\mathrm{R}}^4 L^4 \mathbb{E}\{\lvert X \rvert^4\} \frac{2N^2+1}{2N} P^2,
			\end{equation}
			which verifies the scaling order of $L^4$. The analysis is not presented in the manuscript due to the space constraint.
		\end{response}

		\begin{point}
			The authors are suggested to study the impact of IRS passive beamforming on the waveform design without IRS. For example, they can show the optimized waveforms with versus without IRS to unveil the interplay between them. Or even better, analytically compare the two waveforms.
		\end{point}

		\begin{response}
			Thank you for the suggestion. To see this, we first show one realization of direct channel amplitude (without IRS) and composite channel amplitude (with IRS) for WIT and WPT in Fig.~\ref{fi:channel_amplitude}. It is observed that under the configuration of choice, the WPT-optimized passive beamforming tends to concentrate the channel energy to relatively strong subbands, while the WIT-optimized passive beamforming achieves some balance among all subbands (similar to water-filling at high SNR).

@@

			\begin{figure}[!h]
				\centering
				\resizebox{0.6\columnwidth}{!}{
					\includegraphics{../assets/channel_amplitude}
				}
				\caption{Channel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
				\label{fi:channel_amplitude}
			\end{figure}

### 2021-08-09 main.tex
:pencil: Fix noise notation
:pencil: Update notations
:pencil: Update manuscript

		\begin{subsection}{Received Signal}
			The received superposed signal at the single-antenna UE is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
			\begin{equation}
				y(t) = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})}{e^{j2{\pi}{f_n}{t}}}+y_n(t)\right\},
			\end{equation}
			where $y_n(t)$ is the noise at RF band $n$. Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for decoding.
		\end{subsection}

@@

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}. Therefore, the achievable rate is\footnote{It is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2},\right)}
			\end{equation}
			where $\sigma_n^2$ is the variance of the noise at the RF-band and during the RF-to-baseband conversion on tone $n$.
		\end{subsection}

@@

			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\bar{R}$, $\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
					\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
					\State Set $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

			\begin{algorithm}[!t]
				\caption{GP: Waveform Amplitude and Splitting Ratio.}
				\label{al:gp}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_n$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
					\State Set $g_{m_{\mathrm{I},n}}^{(0)}$, $g_{m_\mathrm{P}}^{(0)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
					\Repeat
						\State $i \gets i + 1$
						\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
						\State Update $g_{m_{\mathrm{I},n}}^{(i)}$, $g_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star}=\rho^{(i)}$
					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star}$, $\boldsymbol{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

			\begin{algorithm}[!t]
				\caption{M-SCA: IRS Phase Shift.}
				\label{al:m_sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\If{$\rho=0$}
						\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
					\Else
						\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
						\Repeat
							\State $i \gets i + 1$
								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
								\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
						\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\EndIf
					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
					\State Set $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}

>>>>

		\begin{subsection}{Received Signal}
			The received superposed signal at the single-antenna UE is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
			\begin{equation}
				y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
			\end{equation}
			where $\tilde{n}_n(t)$ is the noise at RF band $n$. Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for decoding.
		\end{subsection}

@@

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}. Therefore, the achievable rate is\footnote{Requires waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},
			\end{equation}
			where $\sigma_n^2$ is the variance of the noise at the RF-band and during the RF-to-baseband conversion on tone $n$.
		\end{subsection}

@@

			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\bar{R}$, $\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
					\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
					\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

			\begin{algorithm}[!t]
				\caption{GP: Waveform Amplitude and Splitting Ratio.}
				\label{al:gp}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_n$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
					\State Set $g_{m_{\mathrm{I},n}}^{(0)}$, $g_{m_\mathrm{P}}^{(0)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
					\Repeat
						\State $i \gets i + 1$
						\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
						\State Update $g_{m_{\mathrm{I},n}}^{(i)}$, $g_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star}$, $\boldsymbol{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

			\begin{algorithm}[!t]
				\caption{M-SCA: IRS Phase Shift.}
				\label{al:m_sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\If{$\rho=0$}
						\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
					\Else
						\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
						\Repeat
							\State $i \gets i + 1$
								\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
								\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
						\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
					\EndIf
					\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
					\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}
